Collision rates of planetesimals near mean-motion resonances

### 2020-11-12 refereeResponse.txt

The question of applicability:

If I understood the applicability of this work would follow the steps:
1) Once a bump or dip is observed in the dust emission signature of a disk, one would need to assume that this bump or dip reflects the position of the interior 2:1 MMR with a planet.
2) Thus, one would need to look for another dip or bump near what would be the interior 3:1 MMR with that supposed planet.
3) Only then one would be able to guess on the eccentricity and mass of the assumed perturber.

I think this should be clearly said in the conclusions, as well as this idea should be introduced somewhere upfront in the manuscript (maybe in the abstract or introduction). I would not leave to the reader to reach this conclusion. Readers can easily interpret things wrong (especially nowadays where we have so much things to read and we usually read them fast). Did I have the right interpretation or are the author suggesting something different in regards to applicability?

    This is the correct interpretation. The outline at the end of the introduction now explains this. Todo: add a clear outline of this in the conclusions

@@

20) pg.3 rcol P.2 l.34 - "The planetesimal disc extends from 2.2 to 3.8 AU..." - Why not consider the outer disk too? External resonances can be very strong and capture is more likely there.

    This is a good point. Our work was mainly motivated by the non-result seen by Richardson et al. 2000, which is why we focus on interior MMRs here. Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1. TODO: Add a discussion at the end of the paper explaining that exterior MMRs are interesting too.

21) pg.3 rcol P.2 l.41 - This is a minor comment. I am just curious. Why not using alpha = -1 or -0.9 as it seems more common for protoplanetary disks? -1.5 is an approximation for the Minimum Mass Solar Nebula based on the current solar system planets. Observations of proptoplanetary disks sugggest alpha = -1 or -0.9.

    See 19) and 20). While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to suggest that this is the case for solids in the inner planet-forming region. Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models (see Chiang & Laughlin 2013, also Dai et al. 2020)

### 2020-11-12 main.tex
Add calculation of secular forcing timescale

\textbf{Add calculation of secular forcing timescale here}

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a
body, with $M$ being the mean anomaly. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{1999ssd..book.....M}. An important 
point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \text{bf}(ch. 8, pg 338, eq. 8.58) as

>>>>

\textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane. The imaginary and real components of the eccentricity of the jth particle are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}

\begin{eqnarray}\label{eq:kandh}
	h_{j} = e_{j1} sin (g_{1} t + \beta_{1}) + e_{j2} sin (g_{2} t + \beta_{2}) \\ \nonumber
	k_{j} = e_{j1} cos (g_{1} t + \beta_{1}) + e_{j2} cos (g_{2} t + \beta_{2}),
\end{eqnarray}

\noindent \textbf{where  ($e_{j1}$, $e_{j2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}

\begin{eqnarray}\label{eq:pert_matrix}
	A_{jj} = n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(1)} (\alpha) \\ \nonumber
	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha)
\end{eqnarray}.

\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass. The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$. For the case of a Jupiter mass planet at 5.2 au perturbing a test particle, the timescale for secular forcing is approximately 12,000 years at 3 au.}

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a
body, with $M$ being the mean anomaly. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{1999ssd..book.....M}. An important 
point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
